### 2009-10-07 doc/tech_doc/infosys/infosys_technical.tex
Minor language fix
Adapting ISIS documentation to the alternated schema

So Service 1 and 2 are both handled by \textit{InfoRegistrar A} since Service 2 and Service 3 by \textit{InfoRegistrar B}.
In the first step each InfoRegistrar performs information collection from all assigned services sequentially. InfoRegistrars themselves are executing in parallel. After collection  the aggregated information is sent to the corresponding ISISes independently by each other InfoRegistrar.

@@

<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
  xmlns:xsd="http://www.w3.org/2001/XMLSchema"
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2009/isis"
  xmlns:icfg="http://www.nordugrid.org/schemas/ArcConfig/2009/isis"
  targetNamespace="http://www.nordugrid.org/schemas/ArcConfig/2009/isis"
  elementFormDefault="qualified" attributeFormDefault="unqualified"
>

  <xsd:element name="endpoint" type="xsd:anyURI"/>

  <xsd:element name="retry" type="xsd:nonNegativeInteger" minOccurs="0"/>

  <xsd:element name="sparsity" type="xsd:nonNegativeInteger" minOccurs="0"/>

  <xsd:simpleType name="Logger_Type">
    <xsd:restriction base="xsd:string"/>
    <xsd:attribute name="level" type="xsd:string" use="optional"/>
  </xsd:simpleType>
  <xsd:element name="Logger" type="icfg:Logger_Type" minOccurs="0"/>

  <xsd:element name="ETValid" type="xsd:nonNegativeInteger" minOccurs="0"/>

  <xsd:element name="ETRemove" type="xsd:nonNegativeInteger" minOccurs="0"/>

  <xsd:element name="DBPath" type="xsd:string"/>

  <xsd:complexType name="InfoProvider_Type">
    <xsd:sequence>
      <xsd:element name="URL" type="xsd:anyURI"/>
    </xsd:sequence>
  </xsd:complexType>
  <xsd:element name="InfoProvider" type="icfg:InfoProvider_Type" minOccurs="0" maxOccurs="unbounded"/>

@@

<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
  xmlns:xsd="http://www.w3.org/2001/XMLSchema"
  xmlns:iregc="http://www.nordugrid.org/schemas/InfoRegisterConfig/2008"
  targetNamespace="http://www.nordugrid.org/schemas/InfoRegisterConfig/2008"
  elementFormDefault="qualified">

    <xsd:complexType name="InfoRegistrar_Type">
        <!-- This element defines configuration of Information Registration
             active element. This element is located at top level configuration
             document. Each instance if such element instatiates one instance
             of Information \hl{Registrant} active element. -->
        <xsd:sequence>
            <!-- URL specifies contact endpoint of a bootstrap Information
                 Registration service. Further ISIS adresses will be queried
                 from this service. -->
            <xsd:element name="URL" type="xsd:string"/> <!-- maxOccurs="unbounded" -->
            <!-- Optional KeyPath, CertificatePath, ProxyPath and CACertificatesDir are
                 paths to files storing X509 credentials used for establishing connections. -->
            <xsd:element name="KeyPath" type="xsd:string" minOccurs="0"/>
            <xsd:element name="CertificatePath" type="xsd:string" minOccurs="0"/>
            <xsd:element name="ProxyPath" type="xsd:string" minOccurs="0"/>
            <xsd:element name="CACertificatesDir" type="xsd:string" minOccurs="0"/>
            <!-- Retry count. Specifie how many times have an ISIS to timeout to handle it as
                 unavailable. If there is no value specified the default value: 5 will be used. -->
            <xsd:element name="Retry" type="xsd:string" minOccurs="0" maxOccurs="1"/>
        </xsd:sequence>
        <!-- Attribute id may be used to refer to this element -->
        <xsd:attribute name="id" type="xsd:string" use="optional"/>
    </xsd:complexType>
    <xsd:element name="InfoRegistrar" type="iregc:InfoRegistrar_Type"/>

    <xsd:complexType name="Registrar_Type">
        <xsd:sequence>
            <!-- Missing elements means that the default values will be used. -->

            <!-- Period specifies how often registration to be done in minutes.
                 The 0 value means single registration. -->
            <xsd:element name="Period" type="xsd:nonNegativeInteger" minOccurs="0" maxOccurs="1"/>
            <!-- Element defines the unique id of the service propagated outside. -->
            <xsd:element name="ServiceID" type="xsd:string" minOccurs="0" maxOccurs="1"/>
            <!-- This element defines URL of the service as seen from outside. -->
            <xsd:element name="endpoint" type="xsd:string" minOccurs="0" maxOccurs="1"/>
            <!-- This element defines the expiration time of the information provided by the service. -->
            <xsd:element name="expiration" type="xsd:string" minOccurs="0" maxOccurs="1"/>
        </xsd:sequence>
        <!-- Attribute id is to define the previously configured InfoRegistrar to be refered -->
        <xsd:attribute name="id" type="xsd:string" use="required"/>
    </xsd:complexType>

    <xsd:complexType name="InfoRegister_Type">
    <!-- Element for Service element to link it to InfoRegistrar
         elements. It may also override some configuration parameters.
         Presence of this element means that service will be registered
         to ISISes. -->
        <xsd:sequence>
            <!-- This elements specify which registrars must be used
                 for registering services. If there is no such element
                 then registration is done using all registrars. -->
            <xsd:element name="Registrar" type="iregc:Registrar_Type" minOccurs="0" maxOccurs="unbounded"/>
            <!-- Default values for every InfoRegistrar -->

            <!-- Period specifies how often registration to be done in minutes.
                 The 0 value means single registration. -->
            <xsd:element name="Period" type="xsd:nonNegativeInteger" minOccurs="1" maxOccurs="1"/>
            <!-- Element defines the unique id of the service propagated outside. -->
            <xsd:element name="ServiceID" type="xsd:string" minOccurs="0" maxOccurs="1"/>
            <!-- This element defines URL of the service as seen from outside. -->
            <xsd:element name="endpoint" type="xsd:string" minOccurs="1" maxOccurs="1"/>
            <!-- This element defines the expiration time of the information provided by the service. -->
            <xsd:element name="expiration" type="xsd:string" minOccurs="1" maxOccurs="1"/>
        </xsd:sequence>
    </xsd:complexType>
    <xsd:element name="InfoRegister" type="iregc:InfoRegister_Type"/>

    <!-- Configuration element force skipping the Self-Registration -->
    <xsd:element name="NoRegister">
        <xsd:complexType />
    </xsd:element>

@@

\section{Example ISIS service configuration}
\label{annex:example_isis_configuration}
\begin{verbatim}
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
  xmlns:isis="http://www.nordugrid.org/schemas/isis/2008/08"
  xmlns:infosys="http://www.nordugrid.org/schemas/InfoRegisterConfig/2008"
>
  <!-- Various server settings -->
  <infosys:InfoRegistrar id="NorduGridInfosys">
    <!-- Contact and behavior details of the InfoRegsitrar element-->
    <infosys:URL><!-- Available endpoint URL of an ISIS representing the cloud --></infosys:URL>
    <infosys:Retry>4</infosys:Retry>
  </infosys:InfoRegistrar>

@@

    <Service name="isis" id="isis1">
        <isis:DBPath>
            <!-- File location where the database is locally stored -->
        </isis:DBPath>
        <isis:endpoint>
            <!-- The URL where the service can be accessed from outside -->
        </isis:endpoint>
        <isis:InfoProviderISIS>
            <isis:URL>
                <!-- The URL of one or more ISIS where the other ISIS's can be queried. -->
            </isis:URL>
        </isis:InfoProviderISIS>
        <infosys:InfoRegister>
            <infosys:Period>
                <!-- How often should the service be registered. 
                For example: PT75S for 75 seconds -->
            </infosys:Period>
            <infosys:Endpoint>
                <!-- The URL where the service can be accessed from outside -->
            <infosys:Endpoint>
            <infosys:Expiration>
                <!-- The lifetime of the RegEntry provided by the service about itself.
                For example: PT5H for 5 hours -->
            </infosys:Expiration>
            <!-- If there is no specific Registrar defined then every InfoRegistrar
             will be use used during the registration. The period of the repeating 
             registration will be the value given here in every ISIS cloud. -->
        </infosys:InfoRegister>
    </Service>
  </Chain>
</ArcConfig>

>>>>

So Service 1 and Service 2 are handled by \textit{InfoRegistrar A} and Service 2 and Service 3 by \textit{InfoRegistrar B}.
In the first step each InfoRegistrar performs information collection from all assigned services sequentially. InfoRegistrars themselves are executing in parallel. After collection  the aggregated information is sent to the corresponding ISISes independently by each other InfoRegistrar.

@@

<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
  xmlns:xsd="http://www.w3.org/2001/XMLSchema"
  xmlns="http://www.nordugrid.org/schemas/isis/2009/08"
  xmlns:icfg="http://www.nordugrid.org/schemas/isis/2009/08"
  targetNamespace="http://www.nordugrid.org/schemas/isis/2009/08"
  elementFormDefault="qualified" attributeFormDefault="unqualified"
>

  <xsd:element name="KeyPath" type="xsd:string">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Optional KeyPath for SSL connection
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="CertificatePath" type="xsd:string">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Optional CertificatePath for SSL connection
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="ProxyPath" type="xsd:string">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Optional ProxyPath for SSL connection
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="CACertificatesDir" type="xsd:string">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Optional CACertificatesDir for SSL connection
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="endpoint" type="xsd:anyURI">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              The URL where the service can be accessed from outside.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="retry" type="xsd:nonNegativeInteger" default="5">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Retry specifies how many times communication to ISIS have to fail/timeout to start treating it as unavailable.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="sparsity" type="xsd:nonNegativeInteger" default="2">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              It determines the number of neighbors as a function of the actual number of member nodes of the network.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:complexType name="Logger_Type">
    <xsd:simpleContent>
      <xsd:extension base="xsd:string">
        <xsd:attribute name="level" default="INFO">
          <xsd:simpleType>
            <xsd:restriction base="xsd:string">
              <xsd:enumeration value="VERBOSE"/>
              <xsd:enumeration value="DEBUG"/>
              <xsd:enumeration value="INFO"/>
              <xsd:enumeration value="WARNING"/>
              <xsd:enumeration value="ERROR"/>
              <xsd:enumeration value="FATAL"/>
            </xsd:restriction>
          </xsd:simpleType>
        </xsd:attribute>
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>

  <xsd:element name="Logger" type="icfg:Logger_Type">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              File location where the log message is locally stored.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="ETValid" type="xsd:nonNegativeInteger" default="43200">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Soft state database parameter. Time of the valid messages checking period.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="ETRemove" type="xsd:nonNegativeInteger" default="43200">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              Soft state database parameter. Time of the expired messages checking period.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:element name="DBPath" type="xsd:string">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              File location where the database is locally stored.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

  <xsd:complexType name="InfoProvider_Type">
    <xsd:sequence>
      <xsd:element name="URL" type="xsd:anyURI">
          <xsd:annotation>
              <xsd:documentation xml:lang="en">
                  The URL of one or more ISIS where the other ISIS's can be queried.
              </xsd:documentation>
          </xsd:annotation>
      </xsd:element>
    </xsd:sequence>
  </xsd:complexType>

  <xsd:element name="InfoProvider" type="icfg:InfoProvider_Type"/>

@@

<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
  xmlns:xsd="http://www.w3.org/2001/XMLSchema"
  xmlns:iregc="http://www.nordugrid.org/schemas/infosys/2009/08"
  targetNamespace="http://www.nordugrid.org/schemas/infosys/2009/08"
  elementFormDefault="qualified">

    <xsd:complexType name="Registrar_Type">
        <xsd:annotation>
            <xsd:documentation xml:lang="en">
             This element defines configuration of Information Registration.
             active element.
            </xsd:documentation>
        </xsd:annotation>
        <xsd:sequence>

            <xsd:element name="URL" type="xsd:string" minOccurs="1" maxOccurs="unbounded">.
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     URL specifies contact endpoint of a bootstrap Information.
                     Registration service. Further ISIS addresses will be queried.
                     from this service.
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>

            <xsd:element name="ServiceID" type="xsd:string" minOccurs="0" maxOccurs="1">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Element defines the unique id of the service propagated outside.
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>

            <xsd:element name="KeyPath" type="xsd:string"  minOccurs="0" maxOccurs="1">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Optional KeyPath for SSL connection
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>

            <xsd:element name="CertificatePath" type="xsd:string"  minOccurs="0" maxOccurs="1">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Optional CertificatePath for SSL connection
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>
             <xsd:element name="ProxyPath" type="xsd:string"  minOccurs="0" maxOccurs="1">
                 <xsd:annotation>
                     <xsd:documentation xml:lang="en">
                      Optional ProxyPath for SSL connection
                     </xsd:documentation>
                 </xsd:annotation>
             </xsd:element>

            <xsd:element name="CACertificatesDir" type="xsd:string"  minOccurs="0" maxOccurs="1">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Optional CACertificatesDir for SSL connection
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>

            <xsd:element name="Retry" type="xsd:string" minOccurs="0" maxOccurs="1" default="5">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Retry count. Specified how many times have an ISIS to timeout to handle it as.
                     unavailable. If there is no value specified the default value: 5 will be used..
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>
        </xsd:sequence>
    </xsd:complexType>

    <xsd:complexType name="InfoRegister_Type">
        <xsd:annotation>
            <xsd:documentation xml:lang="en">
             Element for Service element to link it to Registrar.
             elements. It may also override some configuration parameters.
             Presence of this element means that service will be registered
             to ISISes.
            </xsd:documentation>
        </xsd:annotation>
        <xsd:sequence>
            <xsd:annotation>
                <xsd:documentation xml:lang="en">
                 This elements specify which registrars must be used
                 for registering services. If there is no such element
                 then registration is done using all registrars.
                </xsd:documentation>
            </xsd:annotation>

            <xsd:element name="Period" type="xsd:duration" minOccurs="1" maxOccurs="1" default="PT3M">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Period specifies how often registration to be done in minutes.
                     The 0 value means single registration.
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>

            <xsd:element name="Endpoint" type="xsd:string" minOccurs="1" maxOccurs="1">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     This element defines URL of the service as seen from outside.
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>

            <xsd:element name="Expiration" type="xsd:string" minOccurs="1" maxOccurs="1" default="PT10M">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     This element defines the expiration time of the information provided by the service.
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>
            <xsd:element name="Registrar" type="iregc:Registrar_Type" minOccurs="0" maxOccurs="unbounded"/>
            <!-- Default values for every Registrar -->
        </xsd:sequence>
    </xsd:complexType>
    <xsd:element name="InfoRegister" type="iregc:InfoRegister_Type"/>

    <xsd:element name="NoRegister">
        <xsd:annotation>
            <xsd:documentation xml:lang="en">
             Configuration element force skipping the Self-Registration
            </xsd:documentation>
        </xsd:annotation>
        <xsd:complexType />
    </xsd:element>

@@

\section{Example ISIS service configuration}
\label{annex:example_isis_configuration}
\begin{verbatim}
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
  xmlns:isis="http://www.nordugrid.org/schemas/isis/2008/08"
  xmlns:infosys="http://www.nordugrid.org/schemas/InfoRegisterConfig/2008"
>
  <!-- Various server settings -->

@@

    <Service name="isis" id="isis1">
        <isis:DBPath>
            <!-- File location where the database is locally stored -->
        </isis:DBPath>
        <isis:endpoint>
            <!-- The URL where the service can be accessed from outside -->
        </isis:endpoint>
        <isis:InfoProviderISIS>
            <isis:URL>
                <!-- The URL of one or more ISIS where the other ISIS's can be queried. -->
            </isis:URL>
        </isis:InfoProviderISIS>
        <infosys:InfoRegister>
            <infosys:Period>
                <!-- How often should the service be registered. 
                For example: PT75S for 75 seconds -->
            </infosys:Period>
            <infosys:Endpoint>
                <!-- The URL where the service can be accessed from outside -->
            <infosys:Endpoint>
            <infosys:Expiration>
                <!-- The lifetime of the RegEntry provided by the service about itself.
                For example: PT5H for 5 hours -->
            </infosys:Expiration>
            <!-- The period of the repeating 
             registration will be the value given here in every ISIS cloud. -->
            <infosys:Registrar>
                <!-- Contact and behavior details of the Registrar element-->
                <infosys:URL><!-- Available endpoint URL of an ISIS representing the cloud --></infosys:URL>
                <infosys:Retry>4</infosys:Retry>        
            </infosys:Registrar>
        </infosys:InfoRegister>
    </Service>
  </Chain>
</ArcConfig>
